% Jacob Conley 2026
% jacob_conley_resume.tex

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{multicol}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
  {\setlength{\leftmargin}{#1}}%
  \item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
  {\setlength{\leftmargin}{-0.5#1}}%
  \item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
  #1 &
  #2 \\
\end{tabular*}}

% and the actual content starts here
\begin{document}

% the header for the resume, name contact info, and location
\begin{center}
{\LARGE \textbf{Jacob Conley}} (he/him)
\end{center}
\begin{center}
\begin{tabular}{ r@{\hspace{10pt}} c@{\hspace{10pt}} l@{\hspace{10pt}} }
  jacob.conley97@gmail.com & \textbullet & github.com/jacobc97 \\
\end{tabular}
  \\ Portland, Oregon
\end{center}

\hrule

\vspace{-0.4em}
\subsection*{Skills}

% skill blurbs, grouped by time
\begin{multicols}{2}
    \begin{itemize*}
        \item +8 years Typescript/Javascript
        \item +4 years of Angular
        \item +4 years of React
      \end{itemize*}
    \columnbreak
    \begin{itemize*}
        \item +6 years of MySql and Postgres
        \item +7 years Agile and Scrum
        \item +6 years Cloud Infrastructure (AWS)
    \end{itemize*}
\end{multicols}

% education section
\vspace{-0.4em}
\subsection*{Education}
\begin{itemize}
  \parskip=0.1em

  \item
  \headerrow
    {\textbf{B.S Computer Science}}
    {\textbf{2019}}
  \\
  \headerrow
    {\emph{Purdue University}}
    {\emph{West Lafayette, IN}}
\end{itemize}

% experience section
\vspace{-0.4em}
\subsection*{Experience}
\begin{itemize}
  \parskip=0.1em

  \item
  \headerrow
    {\textbf{Crunchbase}}
    {\textbf{Remote | Oregon}}
  \\
  \headerrow
    {\emph{Senior Front-End Engineer}}
    {\emph{August 2023 -- Present}}
    \begin{itemize*}
      \item Manages and leads the Crunchbase Front End guild, a group of 10 engineers that work on all front end code across the company. I was responsible for leading the guild meetings, setting the agenda and am currently leading an initiative to optimize the bundle size of our application with a goal of reducing it by 30\%.
      \item Lead the refactor of the team management page. I improved the user experience and design of the page, while also adding new features to allow team admins to better manage their teams. This resulted in a 20\% increase in team management actions taken on the page.
      \item Managed and lead the Scrum/Agile meetings and duties for a team of eleven. I ensured each project lead had their projects planned and tickets pointed. I also was the point of contact if blockers arose and we needed to communicate those to a wider audience.
      \item Planed and designed a new global navigation bar for the Crunchbase application that highlights new features and drove more engagement and trial starts.
      \item Rewrote the chart service used in our application to modernize the look and speed of the charts used within crunchbase.
      \item Lead development for internal agent tools that allowed our agents to provision new user accounts, API keys and other various actions for user accounts, reducing the complexity of their workflows and increasing productivity 15\%.
      \item Lead collaboration between cross-functional teams to rework the export functionality of Crunchbase data into a user digestible csv file.
    \end{itemize*}
    \headerrow
    {\emph{Front-End Engineer}}
    {\emph{April 2022 -- August 2023}}
  \begin{itemize*}
    \item Lead collaboration between cross-functional teams to overhaul the account settings interface, enhancing user experience and streamlining account management processes.
    \item Develop and integrate a self-service feature for API key generation, facilitating increased user autonomy and engagement with platform services.
    \item Implement payment method enhancements, including the incorporation of GooglePay and ApplePay, to simplify and secure user transactions.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Capital One}}
    {\textbf{Virginia}}
  \\
  \headerrow
    {\emph{Senior Associate Software Engineer}}
    {\emph{February 2021 – April 2022}}
  \begin{itemize*}
    \item Designed and implemented a User Interface and Orchestration API to streamline agents’ ability to select options to assist customers calling in. This allowed agents to more effectivly help our customers with the problems they were facing.
    \item Developed a streamlined process that allowed our team to onboard two new agent servicing flows per sprint. This allowed agents to service a larger variety of customers issues each quarter.
    \item Assisted in designing and implementing the ability for customers to save their progress on their small business credit card application. This increased the number of customers that completed our application as they might not have all the information needed on hand.
  \end{itemize*}
  \headerrow
    {\emph{Associate Software Engineer}}
    {\emph{August 2019 – February 2021}}
  \begin{itemize*}
    \item Created various A/B tests to increase the click through rate of the small business credit card application. This increased the number of people successfully filling out the application by 10\%.
    \item Rewrote Small Business Credit Card Application Cypress tests into Playwright tests in a new framework to reduce the test time by 50\%.
    \item Converted the Small Business Credit Card Application over from standard html and javascript over to React.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{By The Book, Inc.}}
    {\textbf{Illinois}}
  \\
  \headerrow
    {\emph{Software Engineer Intern}}
    {\emph{May 2018 -- August 2018}}
    \begin{itemize*}
      \item Created backend using Feathers.js to incorporate a REST API, along with a web tool using React to allow the customer to customize the application.
    \end{itemize*}

  \item
  \headerrow
    {\textbf{By The Book, Inc.}}
    {\textbf{Illinois}}
  \\
  \headerrow
    {\emph{Software Engineer Intern}}
    {\emph{May 2017 -- August 2017}}
    \begin{itemize*}
      \item Worked on Competitor Analysis to determine effective space in the market, designed an IOS application using Objective C and XCode, debugged and modified software components.
    \end{itemize*}
\end{itemize}

% projects and interests section
\vspace{-0.4em}
\subsection*{Peronal Projects and Interests}
\begin{itemize}
  \parskip=0.1em

  \item
  \headerrow
    {\textbf{Developer Community}}
    {\textbf{}}
    Actively engage with the developer community through conference participation. Attend a variety of industry events, fostering collaboration and staying at the forefront of emerging technologies. Passionate open discussions and continuous learning.
  
    \item
    \headerrow
    {\textbf{Open Source Contributions}}
    {\textbf{}}
    Contributes to open-source projects, improving functionality, fixing bugs, and enhancing documentation. Engage with developer communities through code reviews, feature development, and issue triaging. Passionate about collaborative software development and knowledge sharing.
\end{itemize}
\end{document}